---
title: "Final Project"
author: "Vishnu Patel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
library(tidyverse)
library(caTools)
library(purrr)
library(modelr)
library(caret)
library(kableExtra)
```

# DATA

```{r}
NSDUH <- as.tibble(read_csv("final_NSDUH.csv"))
glimpse(NSDUH)

NSDUH %>%
  select(ARRESTED_BOOK)

data1 <- NSDUH %>%
  select(ALC_PAST_YEAR, MRJ_PAST_YEAR, ARRESTED_BOOK, ALC_Age, MRJ_Age, WEEKS_UNEMPL_PY) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data1a <- NSDUH %>%
  select(ALC_PAST_YEAR, MRJ_PAST_YEAR, ARRESTED_BOOK, ALC_Age, MRJ_Age, WEEKS_UNEMPL_PY) %>%
  na.omit() 

data2 <- NSDUH %>%
  select(ARRESTED_BOOK, WEEKS_UNEMPL_PY, HOURS_WORK, ALC_PER_WEEK, ALC_PAST_YEAR) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data2a <- NSDUH %>%
  select(ARRESTED_BOOK, WEEKS_UNEMPL_PY, HOURS_WORK, ALC_PER_WEEK, ALC_PAST_YEAR) %>%
  na.omit()

data3 <- NSDUH %>%
  select(ARRESTED_BOOK, AD_DPREV, DANGER_DELIGHT) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data3a <- NSDUH %>%
  select(ARRESTED_BOOK, AD_DPREV, DANGER_DELIGHT) %>%
  na.omit()

data4 <- NSDUH %>%
  select(ARRESTED_BOOK, SEX, DAYS_SKIPPED_CLASS) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data4a <- NSDUH %>%
  select(ARRESTED_BOOK, SEX, DAYS_SKIPPED_CLASS) %>%
  na.omit() 

data5 <- NSDUH %>%
  select(ALC_SEV_PAST_YEAR, ARRESTED_BOOK) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data5a <- NSDUH %>%
  select(ALC_SEV_PAST_YEAR, ARRESTED_BOOK) %>%
  na.omit() 

data6 <- NSDUH %>%
  select(AGE, ARRESTED_BOOK) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data6a <- NSDUH %>%
  select(AGE, ARRESTED_BOOK) %>%
  na.omit() 

data7 <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data7a <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS) %>%
  na.omit()

data8 <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS, AD_DPREV) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data8a <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS, AD_DPREV) %>%
  na.omit()

data9 <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS, AD_DPREV, WEEKS_UNEMPL_PY, ALC_PAST_YEAR) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))

data9a <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS, AD_DPREV, WEEKS_UNEMPL_PY, ALC_PAST_YEAR) %>%
  na.omit()

tester <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_SEV_PAST_YEAR, AGE, DAYS_SKIPPED_CLASS, AD_DPREV, WEEKS_UNEMPL_PY, ALC_PAST_YEAR, SEX, DANGER_DELIGHT, WEEKS_UNEMPL_PY, HOURS_WORK, ALC_PER_WEEK, ALC_PAST_YEAR) %>%
  na.omit() %>%
  mutate(ARRESTED_BOOK = as.factor(ARRESTED_BOOK))
  
```

## Starter Visualization of Question 2

```{r}
Age_book <- NSDUH %>%
  select(AGE, ARRESTED_BOOK) %>%
  group_by(ARRESTED_BOOK) %>%
  na.omit()
  
Age_book$ARRESTED_BOOK <- as.factor(Age_book$ARRESTED_BOOK)

ggplot(Age_book) +
  geom_bar(aes(x=ARRESTED_BOOK, fill = AGE)) +
  xlab("Ever Been Booked") +
  guides(fill=guide_legend(title="Age")) +
  scale_x_discrete(labels=c('label1', 'label2')) +
  theme_minimal()


age_vis2 <- NSDUH %>%
  select(ARRESTED_BOOK, ALC_PAST_YEAR) %>%
  na.omit()
  
age_vis2$ALC_PAST_YEAR <- as.factor(age_vis2$ALC_PAST_YEAR)
age_vis2$ARRESTED_BOOK <- as.factor(age_vis2$ARRESTED_BOOK)

ggplot(age_vis2) +
  geom_bar(aes(x= ARRESTED_BOOK, fill= ALC_PAST_YEAR)) +
  xlab("Ever Been Booked") +
  theme_minimal() +
  guides(fill=guide_legend(title="Alcohol Past Year Use"))

mod4_tab <- data.frame(
  RMSE = 0.1015524,
  MAE = 0.05965726,
  Accuracy = 0.9733333)
mod4_tab %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


## Modeling

```{r}
set.seed(123)
train.kfold <- trainControl(method = "cv", number = 25)



mod1 <- train(ARRESTED_BOOK ~ MRJ_Age + ALC_Age, data = data1, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod1a <- train(ARRESTED_BOOK ~ MRJ_Age + ALC_Age, data = data1a, method = "glm", trControl = train.kfold, family=binomial(link=logit))

mod2 <- train(ARRESTED_BOOK ~ WEEKS_UNEMPL_PY + ALC_PAST_YEAR, data = data2, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod2a <- train(ARRESTED_BOOK ~ WEEKS_UNEMPL_PY + ALC_PAST_YEAR, data = data2a, method = "glm", trControl = train.kfold, family=binomial(link=logit))

mod3 <- train(ARRESTED_BOOK ~ AD_DPREV, data = data3, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod3a <- train(ARRESTED_BOOK ~ AD_DPREV, data = data3a, method = "glm", trControl = train.kfold, family=binomial(link=logit))

mod4 <- train(ARRESTED_BOOK ~ DAYS_SKIPPED_CLASS, data = data4, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod4a <- train(ARRESTED_BOOK ~ DAYS_SKIPPED_CLASS, data = data4a, method = "glm", trControl = train.kfold, family=binomial(link=logit))

print(mod1)
summary(mod1)

print(mod2)
summary(mod2)

print(mod3)
summary(mod3)

print(mod4)
summary(mod4)


print(mod1a)
print(mod2a)
print(mod3a)
print(mod4a)
print(mod5a)
print(mod6a)
```

# Test Model Extras (No Visualizations Yet)
```{r}
mod5 <- train(ARRESTED_BOOK ~ ALC_SEV_PAST_YEAR, data = data5, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod5a <- train(ARRESTED_BOOK ~ ALC_SEV_PAST_YEAR, data = data5a, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod5

mod6 <- train(ARRESTED_BOOK ~ AGE, data = data6, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod6a <- train(ARRESTED_BOOK ~ AGE, data = data6a, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod6

mod7 <- train(ARRESTED_BOOK ~ AGE + ALC_SEV_PAST_YEAR + DAYS_SKIPPED_CLASS, data = data7, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod7a <- train(ARRESTED_BOOK ~ AGE + ALC_SEV_PAST_YEAR + DAYS_SKIPPED_CLASS, data = data7a, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod7a

mod8 <- train(ARRESTED_BOOK ~ AGE + ALC_SEV_PAST_YEAR + DAYS_SKIPPED_CLASS + AD_DPREV, data = data8, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod8a <- train(ARRESTED_BOOK ~ AGE + ALC_SEV_PAST_YEAR + DAYS_SKIPPED_CLASS + AD_DPREV, data = data8a, method = "glm", trControl = train.kfold, family=binomial(link=logit))
mod8a

mod8a <- train(ARRESTED_BOOK ~ AGE + ALC_SEV_PAST_YEAR + DAYS_SKIPPED_CLASS + AD_DPREV, data = data8a, method = "glm", trControl = train.kfold, family=binomial(link=logit))

```


# Modeling Visualizations
```{r}
predictions1 <- predict(mod1, newdata = data1, type = "raw")
predictions2 <- predict(mod2, newdata = data2, type = "raw")
predictions3 <- predict(mod3, newdata = data3, type = "raw")
predictions4 <- predict(mod4, newdata = data4, type = "raw")

data1 <- mutate(data1, "Predictions" = predictions1)
data2 <- mutate(data2, "Predictions" = predictions2)
data3 <- mutate(data3, "Predictions" = predictions3)
data4 <- mutate(data4, "Predictions" = predictions4)
```

<!--      RMSE       MAE     -->
mod1a  0.3923314  0.3095571
mod2a  0.3238296  0.2115301
mod3a  0.3359712  0.2258661
mod4a  0.1015524  0.05965726
mod5a  0.3072587  0.1888695
mod6a  0.3051467  0.1863853
mod7   0.1061382  0.05392302
mod8   0.0625     0.0625

<!--    Accuracy    -->
mod1    0.8024343
mod2    0.8751303
mod3    0.869548 
mod4    0.9733333
mod5    0.8908351
mod6    0.8908351
mod7    0.967619
mod8    0.9375

Note that the visuals were more accurate in the order of mod4, mod5, mod6, mod2, mod3, mod1 according to the generalized linear model from the caret package. 
* Mod7 and Mod8 contain less than 200 observations in each dataset, which would be challenging to model and visualize. 


## Visualizing our models
```{r}
# Data 1
ggplot(data1) +
  geom_tile(aes(x=MRJ_Age, y= ALC_Age, fill = Predictions)) +
  xlab("First Age of Marijuana Use") +
  ylab("First Age of Alcohol Use")

ggplot(data1) +
  geom_point(aes(x=ALC_Age, y=Predictions)) +
  xlab("First Age of Alcohol Use")

ggplot(data1) +
  geom_point(aes(x=MRJ_Age, y=Predictions)) +
  xlab("First Age of Alcohol Use")

# Data 2
data2$ALC_PAST_YEAR <- as.factor(data2$ALC_PAST_YEAR)

ggplot(data2) +
  geom_boxplot(aes(x=ALC_PAST_YEAR, y=Predictions))

vis2a<- data2 %>%
  group_by(WEEKS_UNEMPL_PY) %>%
  summarize(mean = mean(Predictions))

ggplot(vis2a, aes(x = WEEKS_UNEMPL_PY, y = mean)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(x = "Number of Weeks Unemployed", y = "Mean Predictions") +
  theme_minimal()

# Data 3

vis3a <- data3 %>%
  group_by(AD_DPREV) %>%
  summarize(Mean_Predictions = mean(Predictions)) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
vis3a
# Data 4

# <-- Work in Progress

vis4a<- data4 %>%
  group_by(DAYS_SKIPPED_CLASS) %>%
  summarize(mean = mean(Predictions)) %>%
  filter(DAYS_SKIPPED_CLASS != "0 days")

ggplot(vis4a, aes(x = DAYS_SKIPPED_CLASS, y = mean)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(x = "Number of Days Skipped Class", y = "Mean Predictions") +
  theme_minimal()

ggplot(data4, aes(x = DAYS_SKIPPED_CLASS, y = Predictions)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(x = "Number of Days Skipped Class", y = "Mean Predictions") +
  theme_minimal()
```

```{r}
library(caret)
set.seed(123)
train.kfold <- trainControl(method = "cv", number = 25)

mod1.1 <- train(ARRESTED_BOOK ~ ALC_PAST_YEAR + RACE + AGE_6_CAT + EMPLOYMENT_STATUS18 + TIMES_SOLD_DRUGS + TIMES_STOLE + TIMES_ATTACKED_OTHERS + DANGER_DELIGHT + RISK_FREQ + MRJ_PAST_YEAR + MRJ_EVER + HER_EVER + METH_EVER + DRUG_DISORDER, method = "glm", data = NSDUH, trControl = train.kfold, family=binomial(link=logit))
sprint(mod1.1)
```
